The Astropy Project: xx

### 2021-11-30 src/ms.tex
add new figure

@@

Timeseries, Box Least Squares

TODO: go through What's New pages and identify a few big additions / changes.

@@

Updates!

>>>>

Over the last decade, \python has grown enormously in popularity and has become
a dominant programming language in the astronomical community.

\begin{figure}
    \begin{centering}
        \includegraphics[width=\textwidth]{figures/python-mentions.pdf}
        \caption{
            Yearly full-text mentions of programming languages (indicated in the
            figure legend) in refereed publications in the astronomical
            literature database in the Astrophysics Data System (ADS;
            \citealt{ads}).
            \python has rapidly become the dominant programming language
            mentioned in refereed articles over the last 10 years.
        }
        \label{fig:python-mentions}
    \end{centering}
\end{figure}

@@

\begin{itemize}
    \item Support for representing and transforming velocity data in coordinates, epoch propagation (v3.0)
    \item Improved support for astronomical time series: TimeSeries object (v3.2), Box Least Squares periodogram (v3.1)
    \item Overall improved support of Quantity throughout numpy (v4.0) and scipy
    \item Native support for Time, Quantity, and SkyCoord objects in Astropy tables
    \item TODO: something about WCS, SpectralCoord?
\end{itemize}

@@

New packages and major updates!
